Effects of resonant and random excitations on the proton beam in the Large Hadron Collider, with applications to the design of pulsed hollow electron lenses for active halo control

### 2018-04-20 resex_with_bbl_for_arXiv.tex
Version for arXiv: combined LaTeX source with bbl file; included PDF output.

% bibliography
\bibliography{resex}

>>>>

% bibliography
%\bibliography{resex}

%merlin.mbs apsrev4-1.bst 2010-07-25 4.21a (PWD, AO, DPC) hacked
%Control: key (0)
%Control: author (0) dotless jnrlst
%Control: editor formatted (1) identically to author
%Control: production of article title (0) allowed
%Control: page (1) range
%Control: year (0) verbatim
%Control: production of eprint (0) enabled
\begin{thebibliography}{44}%
\makeatletter
\providecommand \@ifxundefined [1]{%
 \@ifx{#1\undefined}
}%
\providecommand \@ifnum [1]{%
 \ifnum #1\expandafter \@firstoftwo
 \else \expandafter \@secondoftwo
 \fi
}%
\providecommand \@ifx [1]{%
 \ifx #1\expandafter \@firstoftwo
 \else \expandafter \@secondoftwo
 \fi
}%
\providecommand \natexlab [1]{#1}%
\providecommand \enquote  [1]{``#1''}%
\providecommand \bibnamefont  [1]{#1}%
\providecommand \bibfnamefont [1]{#1}%
\providecommand \citenamefont [1]{#1}%
\providecommand \href@noop [0]{\@secondoftwo}%
\providecommand \href [0]{\begingroup \@sanitize@url \@href}%
\providecommand \@href[1]{\@@startlink{#1}\@@href}%
\providecommand \@@href[1]{\endgroup#1\@@endlink}%
\providecommand \@sanitize@url [0]{\catcode `\\12\catcode `\$12\catcode
  `\&12\catcode `\#12\catcode `\^12\catcode `\_12\catcode `\%12\relax}%
\providecommand \@@startlink[1]{}%
\providecommand \@@endlink[0]{}%
\providecommand \url  [0]{\begingroup\@sanitize@url \@url }%
\providecommand \@url [1]{\endgroup\@href {#1}{\urlprefix }}%
\providecommand \urlprefix  [0]{URL }%
\providecommand \Eprint [0]{\href }%
\providecommand \doibase [0]{http://dx.doi.org/}%
\providecommand \selectlanguage [0]{\@gobble}%
\providecommand \bibinfo  [0]{\@secondoftwo}%
\providecommand \bibfield  [0]{\@secondoftwo}%
\providecommand \translation [1]{[#1]}%
\providecommand \BibitemOpen [0]{}%
\providecommand \bibitemStop [0]{}%
\providecommand \bibitemNoStop [0]{.\EOS\space}%
\providecommand \EOS [0]{\spacefactor3000\relax}%
\providecommand \BibitemShut  [1]{\csname bibitem#1\endcsname}%
\let\auto@bib@innerbib\@empty
%</preamble>
\bibitem [{\citenamefont {Holmes}\ \emph {et~al.}(2011)\citenamefont {Holmes},
  \citenamefont {Moore},\ and\ \citenamefont {Shiltsev}}]{tevatron}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
  {Holmes}}, \bibinfo {author} {\bibfnamefont {R.~S.}\ \bibnamefont {Moore}}, \
  and\ \bibinfo {author} {\bibfnamefont {V.}~\bibnamefont {Shiltsev}},\
  }\bibfield  {title} {\enquote {\bibinfo {title} {Overview of the {T}evatron
  collider complex: Goals, operations and performance},}\ }\href {\doibase
  10.1088/1748-0221/6/08/T08001} {\bibfield  {journal} {\bibinfo  {journal}
  {JINST}\ }\textbf {\bibinfo {volume} {6}},\ \bibinfo {pages} {T08001}
  (\bibinfo {year} {2011})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Wenninger}(2017)}]{Wenninger:IPAC:2017}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
  {Wenninger}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Approaching
  nominal performance at {LHC}},}\ }in\  \cite{ipac17},\ pp.\ \bibinfo {pages}
  {13--18}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Br\"{u}ning}\ \emph {et~al.}(2004)\citenamefont
  {Br\"{u}ning}, \citenamefont {Collier}, \citenamefont {Lebrun}, \citenamefont
  {Myers}, \citenamefont {Ostojic}, \citenamefont {Poole},\ and\ \citenamefont
  {Proudlock}}]{lhc_design}%
  \BibitemOpen
  \bibinfo {editor} {\bibfnamefont {O.~S.}\ \bibnamefont {Br\"{u}ning}},
  \bibinfo {editor} {\bibfnamefont {P.}~\bibnamefont {Collier}}, \bibinfo
  {editor} {\bibfnamefont {P.}~\bibnamefont {Lebrun}}, \bibinfo {editor}
  {\bibfnamefont {S.}~\bibnamefont {Myers}}, \bibinfo {editor} {\bibfnamefont
  {R.}~\bibnamefont {Ostojic}}, \bibinfo {editor} {\bibfnamefont
  {J.}~\bibnamefont {Poole}}, \ and\ \bibinfo {editor} {\bibfnamefont
  {P.}~\bibnamefont {Proudlock}},\ eds.,\ \href {\doibase
  10.5170/CERN-2004-003-V-1} {\emph {\bibinfo {title} {{LHC} Design Report}}},\
  \bibinfo {series} {Yellow Reports: Monographs}, Vol.~\bibinfo {volume} {1}\
  (\bibinfo  {publisher} {CERN},\ \bibinfo {address} {Geneva, Switzerland},\
  \bibinfo {year} {2004})\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Apollinari}\ \emph {et~al.}(2017)\citenamefont
  {Apollinari}, \citenamefont {B{\'{e}}jar~Alonso}, \citenamefont
  {Br{\"{u}}ning}, \citenamefont {Fessia}, \citenamefont {Lamont},
  \citenamefont {Rossi},\ and\ \citenamefont {Tavian}}]{hlcdr}%
  \BibitemOpen
  \bibinfo {editor} {\bibfnamefont {G.}~\bibnamefont {Apollinari}}, \bibinfo
  {editor} {\bibfnamefont {I.}~\bibnamefont {B{\'{e}}jar~Alonso}}, \bibinfo
  {editor} {\bibfnamefont {O.}~\bibnamefont {Br{\"{u}}ning}}, \bibinfo {editor}
  {\bibfnamefont {P.}~\bibnamefont {Fessia}}, \bibinfo {editor} {\bibfnamefont
  {M.}~\bibnamefont {Lamont}}, \bibinfo {editor} {\bibfnamefont
  {L.}~\bibnamefont {Rossi}}, \ and\ \bibinfo {editor} {\bibfnamefont
  {L.}~\bibnamefont {Tavian}},\ eds.,\ \href {\doibase 10.23731/CYRM-2017-004}
  {\emph {\bibinfo {title} {High-Luminosity {L}arge {H}adron {C}ollider
  ({HL-LHC}): Technical Design Report V.~0.1}}},\ \bibinfo {series} {Yellow
  Reports: Monographs}\ No.\ \bibinfo {number} {CERN-2017-007-M}\ (\bibinfo
  {publisher} {CERN},\ \bibinfo {address} {Geneva, Switzerland},\ \bibinfo
  {year} {2017})\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Benedikt}\ and\ \citenamefont
  {Zimmermann}(2015)}]{fcc_param_2017}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
  {Benedikt}}\ and\ \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
  {Zimmermann}},\ }\href {https://cds.cern.ch/record/2110736} {\emph {\bibinfo
  {title} {Future Circular Colliders}}},\ \bibinfo {type} {Tech. Rep.}\
  \bibinfo {number} {CERN-ACC-2015-0164}\ (\bibinfo  {institution} {CERN},\
  \bibinfo {address} {Geneva, Switzerland},\ \bibinfo {year}
  {2015})\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Valentino}(2016)}]{helreview_valentino}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
  {Valentino}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {What did we
  learn about halo population during {MD}s and regular operation?}}\ }in\
  \cite{helreview},\ \bibinfo {note} {\url{https://indico.cern.ch/event/567839}
  [Online; accessed 21-Mar-2018]}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Br\"uning}(2016)}]{helreview}%
  \BibitemOpen
  \bibinfo {editor} {\bibfnamefont {O.~S.}\ \bibnamefont {Br\"uning}},\ ed.,\
  \href {https://indico.cern.ch/event/567839} {\emph {\bibinfo {title} {Review
  of the Needs for a Hollow E-lens for the {HL-LHC}}}}\ (\bibinfo
  {organization} {CERN},\ \bibinfo {address} {Geneva, Switzerland},\ \bibinfo
  {year} {2016})\ \bibinfo {note} {\url{https://indico.cern.ch/event/567839}
  [Online; accessed 21-Mar-2018]}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Br{\"{u}}ning}\ \emph {et~al.}(2011)\citenamefont
  {Br{\"{u}}ning}, \citenamefont {Dominguez}, \citenamefont {Myers},
  \citenamefont {Rossi}, \citenamefont {Todesco},\ and\ \citenamefont
  {Zimmermann}}]{helhcparam2011}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {O.}~\bibnamefont
  {Br{\"{u}}ning}}, \bibinfo {author} {\bibfnamefont {O.}~\bibnamefont
  {Dominguez}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Myers}},
  \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Rossi}}, \bibinfo
  {author} {\bibfnamefont {E.}~\bibnamefont {Todesco}}, \ and\ \bibinfo
  {author} {\bibfnamefont {F.}~\bibnamefont {Zimmermann}},\ }\bibfield  {title}
  {\enquote {\bibinfo {title} {{HE-LHC} beam parameters, optics and
  beam-dynamics issues},}\ }in\ \href {\doibase 10.5170/CERN-2011-003.7} {\emph
  {\bibinfo {booktitle} {{EuCARD-AccNet-EuroLumi} Workshop: The High-Energy
  {L}arge {H}adron {C}ollider ({HE-LHC}10)}}},\ \bibinfo {series and number}
  {\bibinfo {series} {Yellow Reports: Conference Proceedings}\ No.\ \bibinfo
  {number} {CERN-2011-003}},\ \bibinfo {editor} {edited by\ \bibinfo {editor}
  {\bibfnamefont {E.}~\bibnamefont {Todesco}}\ and\ \bibinfo {editor}
  {\bibfnamefont {F.}~\bibnamefont {Zimmermann}}}\ (\bibinfo  {publisher}
  {CERN},\ \bibinfo {address} {Geneva, Switzerland},\ \bibinfo {year} {2011})\
  pp.\ \bibinfo {pages} {7--12},\ \Eprint {http://arxiv.org/abs/1108.1617}
  {arXiv:1108.1617 [physics.acc-ph]} \BibitemShut {NoStop}%
\bibitem [{\citenamefont {Molson}\ \emph {et~al.}(2017)\citenamefont {Molson},
  \citenamefont {Bruce}, \citenamefont {Faus-Golfe}, \citenamefont {Fiascaris},
  \citenamefont {Krainer},\ and\ \citenamefont {Redaelli}}]{fcc_coll_ipac2017}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
  {Molson}}, \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Bruce}},
  \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Faus-Golfe}}, \bibinfo
  {author} {\bibfnamefont {M.}~\bibnamefont {Fiascaris}}, \bibinfo {author}
  {\bibfnamefont {A.~M.}\ \bibnamefont {Krainer}}, \ and\ \bibinfo {author}
  {\bibfnamefont {S.}~\bibnamefont {Redaelli}},\ }\bibfield  {title} {\enquote
  {\bibinfo {title} {Status of the {FCC-hh} collimation system},}\ }in\
  \cite{ipac17},\ pp.\ \bibinfo {pages} {64--67}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Bruce}(2016)}]{helreview_bruce}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
  {Bruce}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Alternative
  methods for halo depletion (damper, tune modulation, and wire), long-range
  beam-beam and comparison of their performance / reliability to that of a
  hollow electron lens},}\ }in\  \cite{helreview},\ \bibinfo {note}
  {\url{https://indico.cern.ch/event/567839} [Online; accessed
  21-Mar-2018]}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Stancari}\ \emph {et~al.}(2011)\citenamefont
  {Stancari}, \citenamefont {Valishev}, \citenamefont {Annala}, \citenamefont
  {Kuznetsov}, \citenamefont {Shiltsev}, \citenamefont {Still},\ and\
  \citenamefont {Vorobiev}}]{hel_tevatron_stancari}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
  {Stancari}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Valishev}},
  \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Annala}}, \bibinfo
  {author} {\bibfnamefont {G.}~\bibnamefont {Kuznetsov}}, \bibinfo {author}
  {\bibfnamefont {V.}~\bibnamefont {Shiltsev}}, \bibinfo {author}
  {\bibfnamefont {D.~A.}\ \bibnamefont {Still}}, \ and\ \bibinfo {author}
  {\bibfnamefont {L.~G.}\ \bibnamefont {Vorobiev}},\ }\bibfield  {title}
  {\enquote {\bibinfo {title} {Collimation with hollow electron beams},}\
  }\href {\doibase 10.1103/PhysRevLett.107.084802} {\bibfield  {journal}
  {\bibinfo  {journal} {Phys.\ Rev.\ Lett.}\ }\textbf {\bibinfo {volume}
  {107}},\ \bibinfo {pages} {084802} (\bibinfo {year} {2011})}\BibitemShut
  {NoStop}%
\bibitem [{hlv()}]{hlv13}%
  \BibitemOpen
  \href
  {http://abpdata.web.cern.ch/abpdata/lhc_optics_web/www/hllhc13/round15/index.html}
  {\enquote {\bibinfo {title} {{LHC} optics web: {HLLHCV1.3} --- collision
  round 15~cm optics},}\ }\bibinfo {howpublished}
  {\url{http://abpdata.web.cern.ch/abpdata/lhc_optics_web/www/hllhc13/round15/index.html}
  [Online; accessed 22-Mar-2018]}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Stancari}\ \emph {et~al.}(2015)\citenamefont
  {Stancari}, \citenamefont {Previtali}, \citenamefont {Valishev},
  \citenamefont {Bruce}, \citenamefont {Redaelli}, \citenamefont {Rossi},\ and\
  \citenamefont {Salvachua~Ferrando}}]{hel_cdr}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
  {Stancari}}, \bibinfo {author} {\bibfnamefont {V.}~\bibnamefont {Previtali}},
  \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Valishev}}, \bibinfo
  {author} {\bibfnamefont {R.}~\bibnamefont {Bruce}}, \bibinfo {author}
  {\bibfnamefont {S.}~\bibnamefont {Redaelli}}, \bibinfo {author}
  {\bibfnamefont {A.}~\bibnamefont {Rossi}}, \ and\ \bibinfo {author}
  {\bibfnamefont {B.}~\bibnamefont {Salvachua~Ferrando}},\ }\href
  {https://arxiv.org/abs/1405.2033} {\emph {\bibinfo {title} {Conceptual Design
  of Hollow Electron Lenses for Beam Halo Control in the {L}arge {H}adron
  {C}ollider}}},\ \bibinfo {type} {Tech. Rep.}\ \bibinfo {number}
  {FERMILAB-TM-2572-APC, CERN-ACC-2014-0248}\ (\bibinfo  {institution}
  {Fermilab and CERN},\ \bibinfo {year} {2015})\ \Eprint
  {http://arxiv.org/abs/1405.2033} {arXiv:1405.2033 [physics.acc-ph]}
  \BibitemShut {NoStop}%
\bibitem [{\citenamefont {Shiltsev}\ \emph {et~al.}(2008)\citenamefont
  {Shiltsev}, \citenamefont {Bishofberger}, \citenamefont {Kamerdzhiev},
  \citenamefont {Kozub}, \citenamefont {Kufer}, \citenamefont {Kuznetsov},
  \citenamefont {Martinez}, \citenamefont {Olson}, \citenamefont {Pfeffer},
  \citenamefont {Saewert}, \citenamefont {Scarpine}, \citenamefont {Seryi},
  \citenamefont {Solyak}, \citenamefont {Sytnik}, \citenamefont {Tiunov},
  \citenamefont {Tkachenko}, \citenamefont {Wildman}, \citenamefont {Wolff},\
  and\ \citenamefont {Zhang}}]{Shiltsev:PRSTAB:2008}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {V.}~\bibnamefont
  {Shiltsev}}, \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
  {Bishofberger}}, \bibinfo {author} {\bibfnamefont {V.}~\bibnamefont
  {Kamerdzhiev}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Kozub}},
  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Kufer}}, \bibinfo
  {author} {\bibfnamefont {G.}~\bibnamefont {Kuznetsov}}, \bibinfo {author}
  {\bibfnamefont {A.}~\bibnamefont {Martinez}}, \bibinfo {author}
  {\bibfnamefont {M.}~\bibnamefont {Olson}}, \bibinfo {author} {\bibfnamefont
  {H.}~\bibnamefont {Pfeffer}}, \bibinfo {author} {\bibfnamefont
  {G.}~\bibnamefont {Saewert}}, \bibinfo {author} {\bibfnamefont
  {V.}~\bibnamefont {Scarpine}}, \bibinfo {author} {\bibfnamefont
  {A.}~\bibnamefont {Seryi}}, \bibinfo {author} {\bibfnamefont
  {N.}~\bibnamefont {Solyak}}, \bibinfo {author} {\bibfnamefont
  {V.}~\bibnamefont {Sytnik}}, \bibinfo {author} {\bibfnamefont
  {M.}~\bibnamefont {Tiunov}}, \bibinfo {author} {\bibfnamefont
  {L.}~\bibnamefont {Tkachenko}}, \bibinfo {author} {\bibfnamefont
  {D.}~\bibnamefont {Wildman}}, \bibinfo {author} {\bibfnamefont
  {D.}~\bibnamefont {Wolff}}, \ and\ \bibinfo {author} {\bibfnamefont {X.-L.}\
  \bibnamefont {Zhang}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
  {{T}evatron electron lenses: Design and operation},}\ }\href {\doibase
  10.1103/PhysRevSTAB.11.103501} {\bibfield  {journal} {\bibinfo  {journal}
  {Phys.\ Rev.\ ST Accel.\ Beams}\ }\textbf {\bibinfo {volume} {11}},\ \bibinfo
  {pages} {103501} (\bibinfo {year} {2008})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Fischer}\ \emph {et~al.}(2015)\citenamefont
  {Fischer}, \citenamefont {Gu}, \citenamefont {Altinbas}, \citenamefont
  {Costanzo}, \citenamefont {Hock}, \citenamefont {Liu}, \citenamefont {Luo},
  \citenamefont {Marusic}, \citenamefont {Michnoff}, \citenamefont {Miller},
  \citenamefont {Pikin}, \citenamefont {Schoefer}, \citenamefont {Thieberger},\
  and\ \citenamefont {White}}]{Fischer:PRL:2015}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {W.}~\bibnamefont
  {Fischer}}, \bibinfo {author} {\bibfnamefont {X.}~\bibnamefont {Gu}},
  \bibinfo {author} {\bibfnamefont {Z.}~\bibnamefont {Altinbas}}, \bibinfo
  {author} {\bibfnamefont {M.}~\bibnamefont {Costanzo}}, \bibinfo {author}
  {\bibfnamefont {J.}~\bibnamefont {Hock}}, \bibinfo {author} {\bibfnamefont
  {C.}~\bibnamefont {Liu}}, \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont
  {Luo}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Marusic}},
  \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Michnoff}}, \bibinfo
  {author} {\bibfnamefont {T.~A.}\ \bibnamefont {Miller}}, \bibinfo {author}
  {\bibfnamefont {A.~I.}\ \bibnamefont {Pikin}}, \bibinfo {author}
  {\bibfnamefont {V.}~\bibnamefont {Schoefer}}, \bibinfo {author}
  {\bibfnamefont {P.}~\bibnamefont {Thieberger}}, \ and\ \bibinfo {author}
  {\bibfnamefont {S.~M.}\ \bibnamefont {White}},\ }\bibfield  {title} {\enquote
  {\bibinfo {title} {Operational head-on beam-beam compensation with electron
  lenses in the {R}elativistic {H}eavy {I}on {C}ollider},}\ }\href {\doibase
  10.1103/PhysRevLett.115.264801} {\bibfield  {journal} {\bibinfo  {journal}
  {Phys.\ Rev.\ Lett.}\ }\textbf {\bibinfo {volume} {115}},\ \bibinfo {pages}
  {264801} (\bibinfo {year} {2015})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Shiltsev}(2016)}]{Shiltsev:elens-book:2016}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Vladimir~D.}\
  \bibnamefont {Shiltsev}},\ }\href {\doibase 10.1007/978-1-4939-3317-4} {\emph
  {\bibinfo {title} {Electron Lenses for Super-Colliders}}}\ (\bibinfo
  {publisher} {Springer},\ \bibinfo {year} {2016})\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Fitterer}\ \emph
  {et~al.}(2016{\natexlab{a}})\citenamefont {Fitterer}, \citenamefont
  {Stancari}, \citenamefont {Valishev},\ and\ \citenamefont
  {Redaelli}}]{hel_halo_hllhc_fitterer}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
  {Fitterer}}, \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Stancari}},
  \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Valishev}}, \ and\
  \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Redaelli}},\ }\href
  {\doibase 10.2172/1408322} {\emph {\bibinfo {title} {Simulation Study of
  Hollow Electron Beam Collimation in {HL-LHC}}}},\ \bibinfo {type} {Tech.
  Rep.}\ \bibinfo {number} {FERMILAB-TM-2636-AD}\ (\bibinfo  {institution}
  {Fermilab},\ \bibinfo {year} {2016})\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Fitterer}\ \emph {et~al.}(2017)\citenamefont
  {Fitterer}, \citenamefont {Stancari}, \citenamefont {Valishev}, \citenamefont
  {De~Maria}, \citenamefont {Redaelli}, \citenamefont {Sjobak},\ and\
  \citenamefont {Wagner}}]{hl_halo_ipac2017}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
  {Fitterer}}, \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Stancari}},
  \bibinfo {author} {\bibfnamefont {a.}~\bibnamefont {Valishev}}, \bibinfo
  {author} {\bibfnamefont {R.}~\bibnamefont {De~Maria}}, \bibinfo {author}
  {\bibfnamefont {S.}~\bibnamefont {Redaelli}}, \bibinfo {author}
  {\bibfnamefont {K.}~\bibnamefont {Sjobak}}, \ and\ \bibinfo {author}
  {\bibfnamefont {J.~F.}\ \bibnamefont {Wagner}},\ }\bibfield  {title}
  {\enquote {\bibinfo {title} {Implementation of hollow electron lenses in
  \code{sixtrack} and first simulation results for the {HL-LHC}},}\ }in\
  \cite{ipac17},\ pp.\ \bibinfo {pages} {3795--3798}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Fitterer}\ \emph
  {et~al.}(2016{\natexlab{b}})\citenamefont {Fitterer}, \citenamefont
  {Stancari},\ and\ \citenamefont {Valishev}}]{md_sim_hel_res_ex_fitterer}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
  {Fitterer}}, \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Stancari}},
  \ and\ \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Valishev}},\
  }\href {http://inspirehep.net/record/1496416} {\emph {\bibinfo {title}
  {Effect of Pulsed Hollow Electron-Lens Operation on the Proton Beam Core in
  {LHC}}}},\ \bibinfo {type} {Tech. Rep.}\ \bibinfo {number}
  {FERMILAB-TM-2635-AD}\ (\bibinfo  {institution} {Fermilab},\ \bibinfo {year}
  {2016})\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Zhang}\ \emph {et~al.}(2008)\citenamefont {Zhang},
  \citenamefont {Bishofberger}, \citenamefont {Kamerdzhiev}, \citenamefont
  {Lebedev}, \citenamefont {Shiltsev}, \citenamefont {Thurman-Keup},\ and\
  \citenamefont {Tollestrup}}]{hel_tevatron_abortgap_zhang}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {X.-L.}\ \bibnamefont
  {Zhang}}, \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont {Bishofberger}},
  \bibinfo {author} {\bibfnamefont {V.}~\bibnamefont {Kamerdzhiev}}, \bibinfo
  {author} {\bibfnamefont {V.}~\bibnamefont {Lebedev}}, \bibinfo {author}
  {\bibfnamefont {V.}~\bibnamefont {Shiltsev}}, \bibinfo {author}
  {\bibfnamefont {R.}~\bibnamefont {Thurman-Keup}}, \ and\ \bibinfo {author}
  {\bibfnamefont {A.}~\bibnamefont {Tollestrup}},\ }\bibfield  {title}
  {\enquote {\bibinfo {title} {Generation and diagnostics of uncaptured beam in
  the {F}ermilab {T}evatron and its control by electron lenses},}\ }\href
  {\doibase 10.1103/PhysRevSTAB.11.051002} {\bibfield  {journal} {\bibinfo
  {journal} {Phys.\ Rev.\ ST Accel.\ Beams}\ }\textbf {\bibinfo {volume}
  {11}},\ \bibinfo {pages} {051002} (\bibinfo {year} {2008})}\BibitemShut
  {NoStop}%
\bibitem [{\citenamefont {Stancari}(2014)}]{hel_bends_stancari}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
  {Stancari}},\ }\href {https://arxiv.org/abs/1403.6370} {\emph {\bibinfo
  {title} {Calculation of the Transverse Kicks Generated by the Bends of a
  Hollow Electron Lens}}},\ \bibinfo {type} {Tech. Rep.}\ \bibinfo {number}
  {FERMILAB-FN-0972-APC}\ (\bibinfo  {institution} {Fermilab},\ \bibinfo {year}
  {2014})\ \Eprint {http://arxiv.org/abs/1403.6370} {arXiv:1403.6370
  [physics.acc-ph]} \BibitemShut {NoStop}%
\bibitem [{\citenamefont {Morozov}\ \emph {et~al.}(2012)\citenamefont
  {Morozov}, \citenamefont {Stancari}, \citenamefont {Valishev},\ and\
  \citenamefont {Shatilov}}]{hel_model_polynomial_morozov}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {I.~A.}\ \bibnamefont
  {Morozov}}, \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Stancari}},
  \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Valishev}}, \ and\
  \bibinfo {author} {\bibfnamefont {D.~N.}\ \bibnamefont {Shatilov}},\
  }\bibfield  {title} {\enquote {\bibinfo {title} {Simulation of hollow
  electron beam collimation in the {Fermilab} {Tevatron} collider},}\ }in\
  \href {http://accelconf.web.cern.ch/AccelConf/IPAC2012/papers/moeppb008.pdf}
  {\emph {\bibinfo {booktitle} {Proceedings of the 3rd International Particle
  Accelerator Conference ({IPAC12})}}},\ \bibinfo {series and number} {\bibinfo
  {number} {FERMILAB-CONF-12-126-APC}}\ (\bibinfo  {publisher} {IPAC'12 /
  IEEE},\ \bibinfo {year} {2012})\ pp.\ \bibinfo {pages} {94--96},\ \bibinfo
  {note} {\url{http://accelconf.web.cern.ch/AccelConf/IPAC2012} [Online;
  accessed 21-Mar-2018]}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Stancari}(2018)}]{hel_res_field_stancari_2017}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
  {Stancari}},\ }\href
  {https://indico.cern.ch/event/698949/contributions/2868279/attachments/1590019/2515871/Stancari_LHC_e-lens_meeting_2018-01-26_ebeam_sim_K09.pdf}
  {\enquote {\bibinfo {title} {Electron-beam simulations: Electron-gun emission
  and residual fields from measured profiles},}\ }\bibinfo {howpublished}
  {\url{https://indico.cern.ch/event/698949} [Online; accessed 22-Mar-2018]}
  (\bibinfo {year} {2018}),\ \bibinfo {note} {{CERN} meeting on hollow electron
  lens beam results}\BibitemShut {NoStop}%
\bibitem [{war()}]{warp}%
  \BibitemOpen
  \href@noop {} {\emph {\bibinfo {title} {The \code{warp} particle-in-cell
  code}}},\ \bibinfo {organization} {Lawrence Berkeley National Laboratory},\
  \bibinfo {address} {\url{http://warp.lbl.gov} [Online; accessed
  21-Mar-2018]}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Friedman}\ \emph {et~al.}(2014)\citenamefont
  {Friedman}, \citenamefont {Cohen}, \citenamefont {Grote}, \citenamefont
  {Lund}, \citenamefont {Sharp}, \citenamefont {Vay}, \citenamefont {Haber},\
  and\ \citenamefont {Kishek}}]{Friedman:IEEE-plasma:2014}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
  {Friedman}}, \bibinfo {author} {\bibfnamefont {R.~H.}\ \bibnamefont {Cohen}},
  \bibinfo {author} {\bibfnamefont {D.~P.}\ \bibnamefont {Grote}}, \bibinfo
  {author} {\bibfnamefont {S.~M.}\ \bibnamefont {Lund}}, \bibinfo {author}
  {\bibfnamefont {W.~M.}\ \bibnamefont {Sharp}}, \bibinfo {author}
  {\bibfnamefont {J.~L.}\ \bibnamefont {Vay}}, \bibinfo {author} {\bibfnamefont
  {I.}~\bibnamefont {Haber}}, \ and\ \bibinfo {author} {\bibfnamefont {R.~A.}\
  \bibnamefont {Kishek}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
  {Computational methods in the {W}arp code framework for kinetic simulations
  of particle beams and plasmas},}\ }\href {\doibase 10.1109/TPS.2014.2308546}
  {\bibfield  {journal} {\bibinfo  {journal} {IEEE Trans.\ Plasma Sci.}\
  }\textbf {\bibinfo {volume} {42}},\ \bibinfo {pages} {1321--1334} (\bibinfo
  {year} {2014})}\BibitemShut {NoStop}%
\bibitem [{hel()}]{hel_test_stand_fnal}%
  \BibitemOpen
  \href {https://cdcvs.fnal.gov/redmine/projects/elens/wiki/Test_Stand}
  {\enquote {\bibinfo {title} {The {F}ermilab electron-lens test stand},}\
  }\bibinfo {howpublished}
  {\url{https://cdcvs.fnal.gov/redmine/projects/elens/wiki/Test_Stand} [Online;
  accessed 22-Mar-2018]}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Jo}\ \emph {et~al.}(2018)\citenamefont {Jo},
  \citenamefont {Kim}, \citenamefont {Stancari}, \citenamefont {Chung},\ and\
  \citenamefont {Lee}}]{Jo:PoP:2018}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Y.~H.}\ \bibnamefont
  {Jo}}, \bibinfo {author} {\bibfnamefont {J.~S.}\ \bibnamefont {Kim}},
  \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Stancari}}, \bibinfo
  {author} {\bibfnamefont {M.}~\bibnamefont {Chung}}, \ and\ \bibinfo {author}
  {\bibfnamefont {H.~J.}\ \bibnamefont {Lee}},\ }\bibfield  {title} {\enquote
  {\bibinfo {title} {Control of the diocotron instability of a hollow electron
  beam with periodic dipole magnets},}\ }\href {\doibase 10.1063/1.5018425}
